Flatiron analysis

### 2021-09-08 Rmd/Report 2021.Rmd
Update cleaning and start report

## 1.Clinical summary table
```{r analysis_data}
analysis_data <- Frontline %>% 
  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
  filter(exclude != "1")
```

<span style="color:green">**Table 1 Overall summary demographic/clinical data**</span>
```{r Table 1}
analysis_data %>% 
  select(c(race, raceeth, ethnicity, "vital",
           agecat, "ageatdx",

@@

           "hrd_tissue", "gis_tissue")) %>% 
  tbl_summary() %>% bold_labels()
```

<span style="color:green">**Table 2 Summary demographic/clinical data by race**</span>
```{r Table 2}
analysis_data %>% 
  select(c(race, raceeth, ethnicity, "vital",
           agecat, "ageatdx",

>>>>

## 1.Clinical summary table
```{r analysis_data}

Treatment %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  filter(exclude == "1") %>%
  nrow()

analysis_data <- Treatment %>% 
  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
  filter(exclude != "1")
```

<span style="color:green">**Table 1 Overall summary demographic/clinical data**</span>
```{r Table 1}

library(naniar)
analysis_data %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  select(bmi_at_dx, weight_at_dx, height_at_dx, bsa_at_dx) %>% 
  gg_miss_upset()

analysis_data %>% select(creatinine, CrCl, target_auc, expected_dose) %>% 
  gg_miss_upset()

is.na(analysis_data$CrCl) %>% sum()
is.na(analysis_data$amount) %>% sum()
is.na(analysis_data$target_auc) %>% sum()

analysis_data %>% filter(!is.na(target_auc) & !is.na(expected_dose)) %>%
    distinct(patientid, .keep_all = TRUE) %>% nrow()

# How should I filter??????????????????///
analysis_data %>% 
  select(c(raceeth, "vital",
           agecat, "ageatdx",

           bmi_at_dx, bmi_cat, 
           weight_at_dx, height_at_dx, bsa_at_dx,

@@

           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown")) %>% 
  tbl_summary() %>% bold_labels()
```

<span style="color:green">**Table 2 Summary demographic/clinical data by race**</span>
```{r Table 2}
analysis_data %>% 
  select(c(raceeth, "vital",
           agecat, "ageatdx",
